Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-09 paper/main.tex
[issue 2.28] acknowledgements

We acknowledge support from the 
National Science Foundation Grant No.\ AST-1313415.
RJB acknowledges support as an Associate
within the Center for Advanced Study at the University of Illinois.

@@

>>>>

\changed{
The authors thank the referee for a careful reading of the manuscript
and comments that improved this work.
}
We acknowledge support from the 
National Science Foundation Grant No.\ AST-1313415.
RJB acknowledges support as an Associate
within the Center for Advanced Study at the University of Illinois.

@@

\changed{
This work has made use of the Theano library (http://deeplearning.net/software/theano/),
the Lasagne library (http://lasagne.readthedocs.io/),
and the Nolearn library (http://pythonhosted.org/nolearn/).
}
